
\markboth{BIBLIOGRAFÍA}{BIBLIOGRAFÍA}
\addcontentsline{toc}{chapter}{Bibliografía}

\begin{thebibliography}{99}

    % Academic papers.
    \bibitem{dijkstra} E. W. Dijkstra, ``A note on two problems in connexion with graphs'', {\it Numerische Mathematik}, vol. 1, pp. 269–271, 1959.
    \bibitem{csa} Julian Dibbelt, Thomas Pajor, Ben Strasser, and Dorothea Wagner. 2018. Connection Scan Algorithm. ACM J. Exp. Algorithmics 23, Artículo 1.7 (2018), 56 páginas. \url{https://doi.org/10.1145/3274661}

    % Main specs and manuals.
    \bibitem{gtfs} MobilityData, General Transit Feed Specification (GTFS) Schedule Reference. 2025. \url{https://gtfs.org/schedule/reference}
    \bibitem{gtfs-rt} MobilityData, General Transit Feed Specification (GTFS) Realtime Reference. 2025. \url{https://gtfs.org/realtime/reference}
    \bibitem{postgres} The PostgreSQL Global Development Group, PostgreSQL 17 Documentation. 2025. \url{https://www.postgresql.org/docs/17}
    \bibitem{postgis} PostGIS Project Steering Committee, PostGIS 3.5 Manual. 2025. \url{https://postgis.net/docs/manual-3.5}
    \bibitem{neo4j} Neo4j, Inc., Neo4j Graph Database Operations Manual, v5, 2025. \url{https://neo4j.com/docs/operations-manual/5}
    \bibitem{cypher} Neo4j, Inc., The Cypher Query Language Reference, v5, 2025. \url{https://neo4j.com/docs/cypher-manual/5}
    \bibitem{apoc} Neo4j, Inc., APOC Extended Documentation, v5, 2025. \url{https://neo4j.com/labs/apoc/5}
    \bibitem{neo4j-spatial} Neo4j, Inc., Neo4j-Spatial User Guide, v5, 2025. \url{https://neo4j.com/labs/neo4j-spatial/5}

    % Additional software documentation.
    \bibitem{docker} Docker Inc., Docker Engine User Guide. 2025. \url{https://docs.docker.com/engine}
    \bibitem{python} Python Software Foundation, Python 3.13 Documentation. 2025. \url{https://docs.python.org/3.13}
    \bibitem{pytest} H. Krekel et al., pytest: helps you write better programs, v8.4.x, 2025. \url{https://docs.pytest.org/en/8.4.x}
    \bibitem{hypothesis} D. R. MacIver et al., Hypothesis: Property-based testing for Python. 2025. \url{https://hypothesis.readthedocs.io}
    \bibitem{folium} Folium Developers, Folium: Python data, leaflet.js maps, v0.20.0, 2025. \url{https://python-visualization.github.io/folium}
    \bibitem{pandas} The pandas development team, pandas documentation, v2.3, 2025. \url{https://pandas.pydata.org/pandas-docs/version/2.3}
    \bibitem{qgis} QGIS Development Team, QGIS User Guide, v3.40, 2025. \url{https://www.qgis.org/resources/hub}

    % Wikipedia articles.
    \bibitem{betweenness} Wikipedia, Betweenness centrality. Artículo de wikipedia (\url{https://en.wikipedia.org/wiki/Betweenness_centrality}). Consultado en noviembre de 2025.

\end{thebibliography}

